---
title: "HW2_Alevtina_Bogoliubova-Kuznetsova"
output:
  pdf_document: default
  html_notebook: default
---

## Black Jack probabilities

In your second homework I want you to model Black Jack classic card game.  
You can read rules here: https://www.officialgamerules.org/blackjack  

We have a csv file with a classic 52 card deck.  
Assume that casino has 4 full decks (208 cards).  
Game starts when dealer shuffle all cards and give 2 card for you and 2 for himself.  
To simplify task dealer will always have 2 cards and only you can get additional cards.  
Second thing lets assume that Ace has always 1 point.  
You win if your card sum is more or equal than dealers card sum.  
If your card sum more than 21 you loose.  
Each turn I want you to print game state
  
```{r}
shuffle_deck <- function(deck){
  random <- sample(1:208, size = 208)
  deck <- deck[random, ]
}

draw_card <- function(hand){
  n <- sample.int(208, 1)
  card <- deck[n,]
  hand <- rbind(hand, card[1:3])
  deck <<- deck[-n,]
  return(hand)
}

print_state <- function(p_hand, d_hand, deck){
  d_sum <- sum(d_hand$value)
  p_sum <- sum(p_hand$value)
  cat("Dealer's hand:", fill = T)
  print(d_hand, row.names = F)
  cat(c("sum", d_sum), fill = T)
  cat("Your hand:", fill = T)
  print(p_hand, row.names = F)
  cat(c("sum", p_sum,"\n"))
  
  if (p_sum >= d_sum & p_sum <= 21){
    chances <- 100
  }
  else if (p_sum > 21){
    chances <- 0
  }
  else {
    max <- 21 - p_sum
    min <- d_sum - p_sum
    cards <- sum(deck$value <= max & deck$value >= min)
    chances <- round(cards/nrow(deck)*100)
  }
  cat("chances:", chances, "%", "\n\n")
}  

start_game <- function(p_hand, d_hand, n_deck){
  n_deck <- shuffle_deck(n_deck)
  
  p_hand <<- n_deck[1:2,]
  n_deck <- n_deck[-(1:2),]
  d_hand <<- n_deck[1:2,]
  n_deck <- n_deck[-(1:2),]
  
  print_state(p_hand, d_hand, n_deck)
}

deal <- function(){
  p_hand <<- draw_card(p_hand)
  d_hand <<- d_hand
  print_state(p_hand, d_hand, deck)
}

stop_game <- function(p_hand, d_hand, deck){
  d_sum <- sum(d_hand$value)
  p_sum <- sum(p_hand$value)
  cat("Dealer's hand:", fill = T)
  print(d_hand, row.names = F, col.names=F)
  cat(c("sum", d_sum), fill = T)
  cat("Your hand:", fill = T)
  print(p_hand, row.names = F, col.names=F)
  cat(c("sum", p_sum), fill = T)
  if (p_sum >= d_sum & p_sum <= 21){
    cat("win")
  }
  else{
    cat("loose")
  }
}
```
```{r}
deck <- read.csv('deck.csv')
deck <- deck[rep(seq(nrow(deck)),4),]
p_hand <- data.frame(row.names = c('face', 'suit', 'value'))
d_hand <- data.frame(row.names = c('face', 'suit', 'value'))
```
  
Game 1:  
  
```{r}
start_game(p_hand, d_hand, deck)
```
```{r}
deal()
```
```{r}
stop_game(p_hand, d_hand, deck)
```
  
Game 2:  
  
```{r}
start_game(p_hand, d_hand, deck)
stop_game(p_hand, d_hand, deck)
```
